On the number of tiles visited by a\\ line segment on a rectangular grid

### 2021-12-04 paper.tex
The function g is symmetric in its second and third arguments

% The rounding down (floor) and rounding up (ceiling) operations will be denoted as $\lfloor \cdot \rfloor$ and $\lceil \cdot \rceil$. The notation $[\mathsf S]$ will be used for the Iverson function, which equals $1$ if statement $\mathsf S$ is true and $0$ otherwise.

@@

For $u, v \in \mathbb N$, $\genvar \in \mathbb R^+$, let
\begin{equation}
\label{eq: g def}
g(\genvar, u, v) = \frac 2 \pi \int_{\arcsin \frac u {2\genvar}}^{\arccos \frac v {2\genvar}} \left( \genvar \sin \theta - \frac u 2 \right) \left( \genvar \cos \theta - \frac v 2 \right) \diff \theta.
\end{equation}
Computing the integral in \eqref{eq: g def} and using the identities $\cos^2 \alpha = 1-\sin^2 \alpha$ and $\cos(2\alpha) = 2\cos^2\alpha-1 = 1 - 2\sin^2\alpha$,
\begin{equation}
\label{eq: g fin}
\begin{split}
g(\genvar, u, v) &= \frac 1 {2\pi} \biggl(
\left(\arccos\frac{v}{2\genvar}-\arcsin\frac{u}{2\genvar}\right) u v + 2\genvar^2 + \frac{u^2} 2 + \frac{v^2} 2 \\
& \quad  - u \sqrt{4\genvar^2-v^2} - v \sqrt{4\genvar^2-u^2} \biggr).
\end{split}
\end{equation}

>>>>

The symbols $\lfloor x \rfloor$ and $\lceil x \rceil$ respectively denote the floor (rounding down) and ceiling (rounding up) operations. The functions $\arcsin x$ and $\arccos x$ are defined as their principal branches in the usual way. In particular, the output angles are in $[0, \pi/2]$ for $x \in [0,1]$.
% The notation $[\mathsf S]$ will be used for the Iverson function, which equals $1$ if statement $\mathsf S$ is true and $0$ otherwise.

@@

For $u, v \in \mathbb N$, $\genvar \in \mathbb R^+$, let
\begin{equation}
\label{eq: g def}
g(\genvar, u, v) = \frac 2 \pi \int_{\arcsin \frac u {2\genvar}}^{\arccos \frac v {2\genvar}} \left( \genvar \sin \theta - \frac u 2 \right) \left( \genvar \cos \theta - \frac v 2 \right) \diff \theta.
\end{equation}
Computing the integral in \eqref{eq: g def} and using the identities $\cos^2 \alpha = 1-\sin^2 \alpha$ and $\cos(2\alpha) = 2\cos^2\alpha-1 = 1 - 2\sin^2\alpha$,
\begin{equation}
\label{eq: g fin}
\begin{split}
g(\genvar, u, v) &= \frac 1 {2\pi} \biggl(
\left(\arccos\frac{v}{2\genvar}-\arcsin\frac{u}{2\genvar}\right) u v + 2\genvar^2 + \frac{u^2} 2 + \frac{v^2} 2 \\
& \quad  - u \sqrt{4\genvar^2-v^2} - v \sqrt{4\genvar^2-u^2} \biggr).
\end{split}
\end{equation}
Taking into account that $\arcsin x = \pi/2 - \arccos x$, it follows from \eqref{eq: g fin} that $g(\genvar, u, v) = g(\genvar, v, u)$.
